\documentclass[12pt]{report}
\usepackage{setspace}
\usepackage{here}
\usepackage{cuthesis}
\usepackage{amsmath}
\usepackage[font=small,format=plain,labelfont=bf,up,textfont=up]{caption}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{float}
\usepackage{listings}
\usepackage{courier}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{verbatim}
\usepackage[toc, page]{appendix}
\usepackage[numbers]{natbib}
\usepackage{pbox}
\usepackage{comment}

\author{Guangfu Shi}
\title{Efficient Rendering of Scenes with Dynamic Lighting
             Using a Photons Queue and Incremental Update Algorithm}
\degree{Master of Computer Science}
\dept{Computer Science}       						% default is Comp.Sci.


% Source Code Formatting
\lstset{
         %basicstyle=\footnotesize\ttfamily, % Standardschrift
         basicstyle=\small\ttfamily,
         %numbers=left,               % Ort der Zeilennummern
         numberstyle=\tiny,          % Stil der Zeilennummern
         %stepnumber=2,               % Abstand zwischen den Zeilennummern
         numbersep=5pt,              % Abstand der Nummern zum Text
         tabsize=2,                  % Groesse von Tabs	
         extendedchars=true,         %
         breaklines=true,            % Zeilen werden Umgebrochen
         %keywordstyle=\color{red},
         %frame=t|b,
 %        keywordstyle=[1]\textbf,    % Stil der Keywords
 %        keywordstyle=[2]\textbf,    %
 %        keywordstyle=[3]\textbf,    %
 %        keywordstyle=[4]\textbf,   \sqrt{\sqrt{}} %	
         stringstyle=\color{white}\ttfamily, % Farbe der String
         showspaces=false,           % Leerzeichen anzeigen
         showtabs=false,             % Tabs anzeigen ?
         xleftmargin=17pt,
         framexleftmargin=17pt,
         framexrightmargin=5pt,
         framexbottommargin=4pt,
         %backgroundcolor=\color{lightgray},
         showstringspaces=false,      % Leerzeichen in Strings anzeigen ?
         captionpos=b,
		language=C++,
 }

\begin{document}

\begin{abstract}

Photon mapping is a popular extension to the classic ray tracing algorithm in the field
of realistic image synthesis. Moreover, it benefits from the massive parallelism
computational power brought by recent developments in graphics processor hardware and
programming models. However rendering the scenes with dynamic lights still greatly limits
the performance due to the re-construction at each rendered frame of a kd-tree for the
photons. We developed a novel approach based on the idea that storing the photons data
along with the kd-tree leaf nodes data and implemented new incremental update scheme to
improve the performance for dynamic lighting. The implementation is GPU-based and fully
parallelized. A series of benchmarks with the prevalent existing GPU photon mapping
technique is carried out to evaluate our approach. Our new technique is shown to be
faster when handling scenes with dynamic lights than the existing technique while having
the same image quality.

\end{abstract}

% TF: Need title page & abstract.

\begin{acknowledgments}
First of all, I would like to thank my supervisor, Dr.~Thomas Fevens for his advice, encouragement and support throughout my research. I would also like to thank my parents and my girlfriend Chunxiao Ma who are supportive as always.
\end{acknowledgments}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Body of Thesis goes here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Set the page numbering style
\pagenumbering{arabic}	
\setcounter{page}{1}

%% double spacing
\begin{spacing}{2.0}
	
%-----------------------
% Chapter 1 : Introduction
\include{ch1}

%-------------------------
% Chapter 2:  Background

% Theoretical
%- Radiometry Introduction.
%- BRDF 	
%- Rendering equation and LTE equation
%- Monte-Carlo Ray Tracing.
%- Photon Mapping

% Technical
%- KD-Tree Construction and representation on GPU
%- Photons KNN search using KD-Tree
\include{ch2}

%-------------------------
% Chapter 3: New Approaches
\include{ch3}

%-------------------------
% Chapter 4: Result and Analysis
\include{ch4}	

%o-------------------------
% Chapter 5: Conclusion
\include{ch5}		

%-------------------------
% Appendix
%\include{appendix}				
%-------------------------

\bibliographystyle{plainnat}
\bibliography{refs}

\end{spacing}


\end{document}
